Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-04-06 TEBenchmarkPaper/article.tex
Reword

\begin{abstract}
  We propose a benchmarking methodology to evaluate the efficiency and quality
  of \emph{conjecture generation} by automated tools for \emph{mathematical
    theory exploration}. Our approach uses widely available theorem proving
  tasks as a \emph{ground-truth} corpus, and we demonstrate its use on the
  QuickSpec and IsaCoSy tools, finding that the former takes significantly less
  time to produce significantly more ``interesting'' output. By providing a
  standard, cross-tool evaluation technique we hope to encourage innovation and
  comparison between the disparate approaches currently being pursued, and spur
  improvements similar to those seen in the competitive field of automated
  theorem proving.
%\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\emph{Conjecture generation/formation}, a sub-field of \emph{mathematical theory
  exploration} (MTE), is the open-ended problem of producing conjectures about a
given logical theory which are somehow ``interesting''.

@@

The task of discovering theorems in an arbitrary theory can be
described as the interplay of several processes: (i) formulating new
definitions and concepts; (ii) finding patterns suitable for posing as
conjectures; and (iii) proving that those conjectures are theorems.
The latter is studied extensively in the field of Automated Theorem
Proving (ATP). Far less attention has been paid to automating the
first two tasks, which both Automated Theory Formation (ATF) and
Mathematical Theory Exploration (MTE) address.  We discuss the relationship
between ATF and ATE in historical context in
$\S$\ref{exploration-versus-formation}.

>>>>

\begin{abstract}
  We propose a benchmarking methodology to evaluate the efficiency and quality
  of \emph{conjecture generation} by automated tools for \emph{mathematical
    theory exploration}. Our approach uses widely available theorem proving
  tasks as a \emph{ground-truth} corpus, and we demonstrate its use on the
  QuickSpec and IsaCoSy tools, finding that the former takes significantly less
  time to produce significantly more ``interesting'' output. By providing a
  standard, cross-tool evaluation technique we allow the disparate approaches
  currently being pursued to be more directly compared. Our hope is to encourage
  innovation and improvements similar to those seen in fields like automated
  theorem proving, where the availability of benchmarks encourages healthy
  competition.
%\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\emph{Conjecture generation} is the open-ended task of producing conjectures
about a given logical theory which are somehow ``interesting'', and is studied
as a sub-field of \emph{mathematical theory exploration} (MTE).

@@

The task of automatically proving or disproving a \emph{given} conjecture has
been studied extensively in the field of Automated Theorem Proving (ATP). Less
attention has been paid to \emph{generating} such conjectures automatically,
either from a given set of definitions (the task we will focus on) or where the
definitions are also generated. The fields of Automated Theory Formation (ATF)
and Mathematical Theory Exploration (MTE) both tackle these generation tasks,
and we discuss their relationship in historical context in
$\S$\ref{exploration-versus-formation}.
